---
title: "R Notebook"
output: 
  html_notebook: 
    toc: true
editor_options: 
  markdown: 
    wrap: 72
---





```{r}
source("libs.R")
library(tidyverse)
library(dtplyr)


```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or
by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output
will be saved alongside it (click the *Preview* button or press
*Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the
editor. Consequently, unlike *Knit*, *Preview* does not run any R code
chunks. Instead, the output of the chunk when it was last run in the
editor is displayed.

```{r}
  group_by(gene_name_ms,tumor_type) %>%

    summarise(n=n(),
            
            mean=mean(rpkm),
            sd=sd(rpkm),
            
            se=sd/sqrt(n))
```

#perform t-tests with data in tidy format. Requires broom and tidyverse
Also get summary stats for each group you want. You can then join that
to the p-values after if you want for a slightly data-duplicated df, but
most useful format.

```{r}
library(broom)


results1 <- immune_data_plus_tumor_type %>%
  group_by(gene_name_ms,tumor_type) %>%

  summarise(n=n(),
            
            mean=mean(rpkm),
            sd=sd(rpkm),
            
            se=sd/sqrt(n))




results2<-immune_data_plus_tumor_type%>%
  
  group_by(gene_name_ms)%>%
    
    summarise(
    
      ######### value ~ group ####
      t_test = list(t.test(rpkm ~ tumor_type))) %>%
  
  mutate(p_unadjusted = map_dbl(t_test, ~ .x$p.value)) %>%
  mutate(p_adj_bonferroni = p.adjust(p_unadjusted, method = "bonferroni"),  # Bonferroni correction
         p_adj_fdr = p.adjust(p_unadjusted, method = "fdr"))%>%
  
  select(-t_test)









results3<-results1%>%
  left_join(results2)
  
```

capture plot as ggplot. capture multiple plots into grid. save plot as
pdf.

```{r}
gh<-grid.grabExpr(draw(h1))


ggsave(paste0("k19mf/plots/", "immune-hm-", group_name, ".pdf"),
       plot=gh,
       
       scale = 1,
       dpi=600,
       
       height=.5*nrow(int_mat_z)+8,
       width =.7*ncol(int_mat_z)+10,
       units = "cm",
       
       limitsize = FALSE
       
       )
```

collect all recently written pdfs (can specify time, name, location...)
and combine into 1 pdf.

```{r}
plots<-fs::dir_info("k19mf/plots", full.names = T, pattern="^hm.*\\.pdf$", recurse = F)%>%tibble()%>%
  filter(modification_time>Sys.time()-lubridate::minutes(5))%>%
  arrange(path)%>%
  filter(type=="file")%>%
  pull(path)



qpdf::pdf_combine(plots, output = "k19mf/plots/combined/immune-hms2.pdf")

```




---end