---
title: Useful R Functions
date: "`r Sys.Date()`"
author: go
output:
  html_document:
    highlight: tango
    toc: true
    toc_float: true
    toc_depth: 6

---

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy()
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval = FALSE)
```



### add plot src metadata to plot output. 

Add src metadata below plot to easily check (without having to look at title of pdf doc)



```{r, eval=FALSE, class.source='klippy'}
metadata_text <- paste0("src: ", 
                        rstudioapi::getSourceEditorContext()$path %>%
                          sub("/uufs/chpc.utah.edu/common/home/holmen-group1/otrimskig/","",.) %>%
                          sub("C:/Users/u1413890/OneDrive - University of Utah/garrett hl-onedrive/R/","",.), 
                        "\n", "time: ", 
                        lubridate::round_date(Sys.time(), "second"))

text_grob <- textGrob(metadata_text, x=.05, just="left", gp = gpar(fontsize = 9, col = "gray30"))

p3src<-grid.arrange(p3, text_grob, ncol = 1, heights = c(3, 0.3))


```






### how to save a ggplot or other grob to pdf. 

This below is useful because it adds a title to the metadata of the pdf file, which prints the R script path and date-time of generation.


```{r, eval=FALSE, class.source='klippy'}
ggsave("file_path_output",
       
       title=paste0("src: ",
                      
                      rstudioapi::getSourceEditorContext()$path%>%
                        sub("/uufs/chpc.utah.edu/common/home/holmen-group1/otrimskig/","",.)%>%
                      sub("C:/Users/u1413890/OneDrive - University of Utah/garrett hl-onedrive/R/","",.),
                      
                      " at ", 
                      
                      lubridate::round_date(Sys.time(), "second")
         ),
         
       plot=plot_object,
       limitsize = FALSE,
       
       
       height=10,
       width=30,
       scale = .5,
       dpi=600,
       
       
       
)
```

### some super useful dplyr calls

```{r}
#sorts columns by names
select(sort(names(.)))

#remove columns with all NA values
select(where(~ !all(is.na(.))))


# Filter out columns where all values are 0
df_filtered <- df %>%
  select(where(~ !all(. == 0)))


#change column names
 rename_with(~ str_replace(., "^X", "x"), .cols = starts_with("X"))
 
 
 
 
#helpful to turn specific date formats into actual dates,
#useful where there are mixed columns
mutate(injection_date_1 = lubridate::as_date(str_extract(injection_date, "^\\d{4}-\\d{2}-\\d{2}$")))

```

### google sheets usage

```{r}
##################################
#sheet id and sheet name to read in from sheets. 

sheet_id<-"1bdya6WH1KA-w3ziKprTpbxd-S1zJh1zPef754b8eDKY"
name_of_sheet<-"lab_samples"



#################################



############
#authorize user.
gs4_auth(email = "gotrimski@gmail.com")

#read input sheet
sheets_df<-read_sheet(sheet_id, 
                    sheet = name_of_sheet)%>%
  mutate(across(1:last_col(), as.character))%>%
  
  #then replace all "NULL" with NA. 
  mutate(across(1:last_col(), function(x){na_if(x, "NULL")}))%>%
  
  janitor::clean_names()


```

```{r}
  group_by(gene_name_ms,tumor_type) %>%

    summarise(n=n(),
            
            mean=mean(rpkm),
            sd=sd(rpkm),
            
            se=sd/sqrt(n))
```

### perform t-tests with data in tidy format. 

Requires broom and tidyverse Also get summary stats for each group you want. You can then join that to the p-values after if you want for a slightly data-duplicated df, but most useful format.

```{r}
library(broom)


results1 <- immune_data_plus_tumor_type %>%
  group_by(gene_name_ms,tumor_type) %>%

  summarise(n=n(),
            
            mean=mean(rpkm),
            sd=sd(rpkm),
            
            se=sd/sqrt(n))




results2<-immune_data_plus_tumor_type%>%
  
  group_by(gene_name_ms)%>%
    
    summarise(
    
      ######### value ~ group ####
      t_test = list(t.test(rpkm ~ tumor_type))) %>%
  
  mutate(p_unadjusted = map_dbl(t_test, ~ .x$p.value)) %>%
  mutate(p_adj_bonferroni = p.adjust(p_unadjusted, method = "bonferroni"),  # Bonferroni correction
         p_adj_fdr = p.adjust(p_unadjusted, method = "fdr"))%>%
  
  select(-t_test)









results3<-results1%>%
  left_join(results2)
  
```

### capture plot as ggplot. 

capture multiple plots into grid. save plot as pdf.

```{r}
gh<-grid.grabExpr(draw(h1))


ggsave(paste0("k19mf/plots/", "immune-hm-", group_name, ".pdf"),
       plot=gh,
       
       scale = 1,
       dpi=600,
       
       height=.5*nrow(int_mat_z)+8,
       width =.7*ncol(int_mat_z)+10,
       units = "cm",
       
       limitsize = FALSE
       
       )
```

collect all recently written pdfs (can specify time, name, location...) and combine into 1 pdf.

```{r}
plot_paths <- fs::dir_info("nf1g/surv/plots", regexp = "\\.pdf$", recurse = FALSE) %>%
  #filter(modification_time>Sys.time()-lubridate::minutes(1))%>%
  filter(type == "file") %>%
  arrange(path) %>%
  tibble()


qpdf::pdf_combine(plots, output = "k19mf/plots/combined/immune-hms2.pdf")

```

```{r}
mutate(
  consistent_date = case_when(
    str_detect(injection_date, "/") ~ mdy(injection_date),
    str_detect(injection_date, "-") ~ ymd(injection_date),
    TRUE ~ NA_Date_
  )
)
```

---end

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
